### 2022-11-17 manuscript.tex
Adding output settings to trigger the rendering action [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3490551921

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/e1d16866f2990cbb44fa4baf16633ca0e6a67556/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/e1d16866f2990cbb44fa4baf16633ca0e6a67556}{SORTEE-Github-Hackathon/manuscript@e1d1686}
on November 17, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31}{SORTEE-Github-Hackathon/manuscript@8d4190c}
on November 17, 2022.
